\documentclass{letter}

\textheight=10in
\textwidth=7.3in
\topmargin=-1.0in
\headheight=0.2in
\headsep=0.2in
\oddsidemargin=-0.5in
\evensidemargin=-0.9in
\marginparpush=1in
\marginparsep=1in
\marginparwidth=1in
\footskip=0in

\parindent=0in

\newcommand{\experience}[4]{&& \\
\textit{#1} \hspace{0.2in} & \textbf{#2} & \textbf{#3} \\
& \textit{#4} & \\}
\newcommand{\subexperience}[1]{& #1 & \\}
\newcommand{\subsubexperience}[1]{& #1 & \\}

\newcommand{\education}[3]{\hspace{0.5in}\textbf{#1, #2 (#3)}\\}
\newcommand{\subeducation}[1]{\hspace{1in}#1\\}

\begin{document}
\thispagestyle{empty}

\LARGE
\begin{center}Palmer Dabbelt\end{center}
\normalsize

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
  Redwood City, CA& 339-225-1919 \\
  94062 & palmer@dabbelt.com \\
  \hline
\end{tabular*}\\

\vspace{0.2in}
Looking for a bigger challenge.
\vspace{0.2in}

\textbf{Experience}\\
\begin{tabular*}{\textwidth}{l l @{\extracolsep{\fill}} r}
  \experience{2019-current}{RISC-V Foundation}{}{Chair of UNIX-Class Platform Specification}
  \subexperience{In the process of defining a specification for Linux-capable systems}

  \experience{2018-current}{SiFive}{San Mateo, CA}{Director of Software}
  \subexperience{Technical lead and manager for all software at SiFive}
  \subexperience{Scaled the software team from one engineer to ten}
  \subexperience{Responsible for two acqui-hires of software teams}
  \subexperience{Responsible for software product definition and implementation}

  \experience{2017-current}{SiFive}{San Mateo, CA}{Software Engineer}
  \subexperience{Maintainer of the RISC-V ports of binutils, GDB, GCC, glibc, Linux, and QEMU}
  \subexperience{Pre-silicon verification sign-off for SiFive chips}
  \subexperience{Wrote the manufacturing test suite for the HiFive Unleashed}
  \subexperience{Responsible for solving customer-specific software emergencies}

  \experience{2016-current}{RISC-V Foundation}{}{Vice-chair of Software Working Group}
  \subexperience{Coordinate the RISC-V software ecosystem}
  \subexperience{Give talks around the world to evangelize RISC-V}
  \subexperience{Major success: RISC-V Fedora and Debian ports}

  \experience{2013-2014}{CS194-24 TA}{Berkeley, CA}{TA (Class Title: Operating Systems)}
  \subexperience{The course is really "intro to Linux hacking", some QEMU development}
  \subexperience{Wrote labs, ran discussion section, wrote/graded exams}
  \subexperience{Labs: HTTP server, file system, scheduler, ethernet driver}

  \experience{2011-2013}{Tilera}{Westborough, MA}{Software Engineer}
  \subexperience{Ported the Hotspot JVM to Tilera's Tile-Gx processors}

  \experience{2009-11}{Nuvixa}{Champaign, IL}{Software Engineer}
  \subexperience{Startup doing depth assisted image processing}
  \subexperience{Optimization of code for x86 processors}
  \subexperience{Network video streaming protocol}
  
  \experience{2009-11}{ECE391 Lab TA}{Champaign, IL}{Lab TA (Class Title: Computer Systems Engineering)}
  \subexperience{Write a single user, multi tasking (with virtual memory) OS}
  \subexperience{I help students with debugging code and learn concepts}
\end{tabular*}\\
\vspace{0.2in}

\textbf{Projects}
\begin{itemize}
\item Original author of Freedom Metal, SiFive's bare-metal portability library.
\item Announced the first Linux-capable RISC-V chip, in addition to bringing up
  the software for it and writing the first manufacturing test bench for the
  eventual production run of the board.
\item Original contributor and maintainer of the RISC-V ports of binutils, GDB,
  GCC, glibc, Linux and QEMU. 
\item Architecture/RTL lead on a RISC-V processor on TSMC's 16nm FinFET+
  process that includes some DSP extensions.
\item RTL lead on a dual-core RISC-V processor with integrated vector units on
  ST's 28nm FDSOI process that includes integrated power management features
  and low-speed serial links.
\item Ported the Hotspot JVM (and Sun's OpenJDK) to Tilera's Tile-Gx
  processors.  Our team consisted of two people.  I started mid-way
  through the process, with a functional port of Hotspot's interpreter
  to Tile-Pro (the previous generation of Tilera chips), but I the two
  of us ported Hotspot's interpreter and the C2 server compiler to
  Tile-Gx.
\item Created a superscalar out of order implementation of the LC3b
  processor in VHDL.  The processor has split L1 caches and a unified
  L2 cache.  It uses Tomasulu's algorithm to achieve out of order
  execution.  This was a group project which ended up winning me the
  411 design competiton.
\item Single user cluster operating system using serial interconnects
  for x86.  Written in C and x86 ASM.  In addition, for this project I
  wrote an implementation of packet-switched networking over serial
  ports, a network aware scheduler, synchronization constructs, and an
  implementation of shared memory over the network.  This project won
  me honorable mention in the ECE391 Programming Contest.
\item Created and implemented a real-time video streaming protocol
  over UDP on GNU/Linux.  Written in C.  In addition, I wrote code to
  interface with V4L USB video capture on Linux and code to interface
  with OpenGL on Linux.
\item Created and implemented a real-time background subtraction
  algorithm using depth cameras.  I wrote an implementation using C on
  GNU/Linux and am currently working on an implementation using C++ on
  Win32, which will be commercial quality code.  I have a patent on
  this algorithm.
\end{itemize}

\textbf{Awards}
\begin{itemize}
\item EE Times "Most Respected Private Semiconductor Company" awarded to SiFive, 2018
\item EE Times "Design Team of the Year" awarded to Tilera, 2012
\item $4^{\mathrm{th}}$ in ECE498 (CUDA) Programming Contest, Spring 2010
\item Won ECE411 Design Competiton, Fall 2009
\item Honorable Mention in ECE391 Programming Contest, Spring 2009
\end{itemize}
\vspace{0.2in}

\textbf{Education}\\
\begin{tabular*}{\textwidth}{l l @{\extracolsep{\fill}} r}
  \experience{August 2012 - March 2017}{University of California}{Berkeley, CA}{MS Computer Science}
  \experience{August 2008 - June 2011}{University of Illinois}{Champaign, IL}{BS Computer Engineering}
  \subexperience{GPA: 3.6}
\end{tabular*}
\end{document}
